---
title: "In-class_Ex07"
author: "Sherinah Rashid"
date: '5 May 2023'
editor: visual
format:
  html: 
    code-fold: true
    code-summary: "Show code"
    code-overflow: wrap
    code-block-bg: true
    code-block-border-left: "#18661c"
execute:
  eval: true
  echo: true
  warning: false
  freeze: auto
---

In today's in class exercise, Prof shared with us how to plot a horizon graph. 

A horizon graph is an analytical graphical method specially designed for visualising large numbers of time-series. It aims to overcome the issue of visualising highly overlapping time-series. 

In this section, you will learn how to plot a [horizon graph](http://www.perceptualedge.com/articles/visual_business_intelligence/time_on_the_horizon.pdf) by using [ggHoriPlot package](https://rivasiker.github.io/ggHoriPlot/).


# Import the R Packages

```{r}
pacman::p_load(ggHoriPlot, ggthemes, tidyverse)
```

# Loading the dataset

For the purpose of this hands-on exercise, [Average Retail Prices Of Selected Consumer Items](https://tablebuilder.singstat.gov.sg/table/TS/M212891) will be used. 

```{r}
averp <- read_csv("data/AVERP.csv") %>%
  mutate(`Date` = dmy(`Date`))
```

::: callout-note  
By default, read_csv will import data in Date field as Character data type. dmy() of lubridate package to parse the Date field into appropriate Date data type in R.
:::

# Plotting the horizon graph

Note that there is no output for the below code chunk! Refer to the in-line comments for the logic behind the code. 

```{r}
averp %>% 
  #filter the data as necessary
  filter(Date >= "2018-01-01") %>%
  #we want to ensure only the filtered data will be placed into ggplot, so we do the above first before coding the line below
  ggplot() +
  geom_horizon(aes(x = Date, y=Values), 
               origin = "midpoint", 
               horizonscale = 6)+
  #we placed in ` because there's a space in the csv file for the header! So we put in the ` to ensure that it recognises as one field name. The ~ is to state it as a facet grid. 
  facet_grid(`Consumer Items`~.) +
    theme_few() +
  scale_fill_hcl(palette = 'BuPu') +
  theme(panel.spacing.y=unit(0, "lines"), strip.text.y = element_text(
    size = 5, angle = 0, hjust = 0),
    legend.position = 'none',
    axis.text.y = element_blank(),
    axis.text.x = element_text(size=7),
    axis.title.y = element_blank(),
    axis.title.x = element_blank(),
    axis.ticks.y = element_blank(),
    panel.border = element_blank()
    ) +
    scale_x_date(expand=c(0,0), date_breaks = "3 month", date_labels = "%b%y") +
  ggtitle('Average Retail Prices of Selected Consumer Items (Jan 2018 to Dec 2022)')

```


```{r}

```





